---
title: "Provisioning"
author: "Val"
date: "5/29/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../r/utils/functions.R")
library(tidyr)
library(dplyr)
library(tidyverse)
library(missMDA)
library(FactoMineR)
library(FactoInvestigate)
library(Factoshiny)
library(caret)
library(leaps)
library(tibble)
```

## Principal Component Analysis

Load the data set

```{r dataset}
staticPathWB <- "./Static/WB/pivoted/"
withOutcomes <- read.csv("../../data/after_clean/data_frames/withOutcomes.csv")
energyuse <- read.csv("../../data/after_clean/wb_pivoted/formatted/energyuse.csv")
withEnergyUseList <- list(withOutcomes, energyuse)
withEnergyUse <- withEnergyUseList %>% reduce(left_join, by=c('Country.Code', 'Year'))
wbJoinedSorted <- withOutcomes %>% arrange(Country.Code, Year)
```
Separate columns with few observations (less than 10k)

```{r fewobs}
sort(colSums(is.na(wbJoinedSorted)))

values_worry_cols <- c("WorryGovPrivacy", "WorryWar", "WorryTerrorist", "WorryCivilWar")
values_worry_educ <- "WorryEduc" # only this not excluded
values_conf_cols <- c("ConfCourts", "ConfParties", "ConfCivilService", "ConfGov", "ConfParliament")
values_accept_cols <- c("BeatWife", "Violence", "TaxCheat", "AcceptBribe", "StealProp")
values_member_cols <- c("SelfHelpOrgMember", "ProfOrgMember", "CharityOrgMember", "ConsumOrgMember", "EnvOrgMember")
values_religion_cols <- c("BelieveGod")
values_child_faith <- c("ChildFaith")
all_values_cols <- c(values_worry_cols, values_conf_cols, values_accept_cols, values_member_cols, values_religion_cols, values_worry_educ, values_child_faith)

few_obs_cols <- c("femalemanager", "informal", "gendergap")

## Income columns. We control for these by using income groups so safe to remove
income_cols <- c("gdppercap", "gnipercap")
wealth_cols <- c("wealth", "wealthincome")

# testDFComplete <- wbJoinedSorted %>% filter(Country.Name != "")
# testDFSelectedValues <- wbJoinedSorted %>% select(!c(values_worry_cols, values_conf_cols,values_religion_cols, values_member_cols, few_obs_cols)) %>% filter(Country.Name != "")
#testDFNoValuesNoFewObs <- wbJoinedSorted %>% select(!c(all_values_cols, few_obs_cols)) %>% filter(Country.Name != "")
testDFNoValuesNoFewObsNoIncome <- wbJoinedSorted %>% select(!c(all_values_cols, few_obs_cols, income_cols)) %>% filter(Country.Name != "")
#testDFSelectedValuesNoIncome <- wbJoinedSorted %>% select(!c(values_worry_cols, values_conf_cols,values_religion_cols, values_member_cols, few_obs_cols, income_cols)) %>% filter(Country.Name != "")
#testDFWithOutcomesSelectedValuesNoIncome <- wbJoinedSorted %>% select(!c(values_worry_cols, values_conf_cols,values_religion_cols, values_member_cols, few_obs_cols, income_cols)) %>% filter(Country.Name != "") %>% select(!c("X","X.1","X.2", "X.3", "X.4"))
provisioning <- testDFWithOutcomesSelectedValuesNoIncome
sort(colSums(is.na(provisioning)))
```

Finish preparing the data set

```{r finaldata}
# testDF$ID <- paste(testDF$Year, testDF$Country.Name, sep=" - ")
# sort(table(filter(testDF, !is.na(WorryEduc))$Year))

#testDF_filtered <- testDFSelectedValuesNoIncome %>% filter(region == "Europe & Central Asia") %>% filter(Year == 2018) %>% select(!c("X","X.1","X.2", "X.3", "X.4"))
testDF_filtered <- provisioning
# filter one year: testDFNoValuesNoFewObsNoIncome %>% filter(Year == 2018)
# filter one income group: testDFNoValuesNoFewObsNoIncome %>% filter(incomegroup == "High income")
# filter one region: testDFNoValuesNoFewObsNoIncome %>% filter(region == "Europe & Central Asia")

testDF_indexed <- testDF_filtered %>% column_to_rownames(., var = 'Country.Name')
var_df <- testDF_filtered %>% select(!c("incomegroup", "region")) %>% rename(ID = "X.5")
countryYear <- var_df %>% select(c("Country.Code", "Year")) 
incomeGroupAndRegion <- testDF_filtered %>% select(c("incomegroup", "region"))
var_df[var_df == ".."] <- NA
energyuse[energyuse == ".."] <- 0
cols <- names(var_df)[11:66]
var_df$concentration <- gsub(",",".",var_df$concentration)
var_df[cols] <- lapply(var_df[cols], as.numeric)
provisioning <- cbind(var_df, incomeGroupAndRegion)
```

Conduct Principal Component Analysis (PCA) on the formatted and cleaned data set

```{r impute}
testDF_toimpute <- var_df %>% select(!c("Country.Code", "Year")) %>% select_if(function(v) var(v, na.rm=TRUE) != 0) 
testDF_imputed <- imputePCA(testDF_toimpute, ncp=2, maxiter=1000000)
```

Conduct feature selection (caret) on imputed data
```{r gpt}
outcomesWithCountries <- cbind(countryYear, outcomes)
lifeExpectancyWithCountries <- outcomesWithCountries %>% select(c("Country.Code", "Year", "lifeexpectancy"))

indicatorsWithCountries <- cbind(countryYear, exceptOutcomes)
energyuseWithCountries <- energyuse %>% filter(Country.Code != "")
energyUseNoNA <- energyuseWithCountries %>% filter(energyuse != 0)
indicatorsWithEnergyUseList <- list(energyUseNoNA, indicatorsWithCountries) 
indicatorsWithEnergyUse <- lifeExpectancyWithEnergyUseList %>% reduce(left_join, by=c('Country.Code', 'Year'))
lifeExpectancyWithIndicatorsEUseList <- list(indicatorsWithEnergyUse, lifeExpectancyWithCountries)
lifeExpectancyWithIndicatorsEUse <- lifeExpectancyWithIndicatorsEUseList %>% reduce(left_join, by=c('Country.Code', 'Year'))
lifeExpectancyOverEnergyUseWithCountries <- lifeExpectancyWithEnergyUseWithCountries %>% mutate(lifeexpectancy_over_energy = lifeexpectancy / as.numeric(energyuse)) %>% select(!c("lifeexpectancy", "energyuse"))
withLEOverEnergyUse <- lifeExpectancyWithIndicatorsEUse %>% mutate(lifeexpectancy_over_energy = lifeexpectancy / as.numeric(energyuse)) %>% select(!c("lifeexpectancy", "energyuse"))
write.csv(withLEOverEnergyUse, "indicatorsWithEnergyuse.csv")
withLEOverEnergyUse
#write.csv(outcomesWithCountries, "outcomes.csv")
#write.csv(lifeExpectancyWithCountries, "lifeexpectancy.csv")
#write.csv(indicatorsWithCountries, "indicators.csv")
#write.csv(energyuseWithCountries, "energyuse.csv")
#leOverEnergyAndIndicators <- cbind(countryYear, exceptOutcomes, energyUseNoNA)
```

```{r caret}
imputed <- testDF_imputed$completeObs
index <- which(colnames(imputed) == "lifeexpectancy")
exceptOutcomes <- imputed[,8:55]
outcomes <- imputed[,56:63]
lifeExpectancy <- imputed[,index]
set.seed(10)
ctrl <- rfeControl(functions = lmFuncs,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)
lmProfile <- rfe(exceptOutcomes, lifeExpectancy,
                 sizes = 10,
                 rfeControl = ctrl,
                 na.action = na.omit)
```
```{r bestsubset}
scaled_withLEOverEnergyUse <- withLEOverEnergyUse %>% select(!c("Country.Code", "Year"))
for_best_subset <- scaled_withLEOverEnergyUse %>% mutate_all(~(scale(.) %>% as.vector))
Best_Subset <-
    regsubsets(lifeexpectancy_over_energy~.,
               data = for_best_subset,
               nbest = 1,      # 1 best model for each number of predictors
               nvmax = 48,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary_best_subset <- summary(Best_Subset)

# courtesy http://sthda.com/english/articles/37-model-selection-essentials-in-r/155-best-subsets-regression-essentials-in-r for the functions below

# id: model id
# object: regsubsets object
# data: data used to fit regsubsets
# outcome: outcome variable
get_model_formula <- function(id, object, outcome){
  # get models data
  models <- summary(object)$which[id,-1]
  # Get outcome variable
  #form <- as.formula(object$call[[2]])
  #outcome <- all.vars(form)[1]
  # Get model predictors
  predictors <- names(which(models == TRUE))
  predictors <- paste(predictors, collapse = "+")
  # Build model formula
  as.formula(paste0(outcome, "~", predictors))
}
get_model_formula(3, Best_Subset, "lifeexpectancy_over_energy")
get_cv_error <- function(model.formula, data){
  set.seed(1)
  train.control <- trainControl(method = "cv", number = 5)
  cv <- train(model.formula, data = data, method = "lm",
              trControl = train.control)
  cv$results$RMSE
}
model.ids <- 1:48
cv.errors <-  map(model.ids, get_model_formula, Best_Subset, "lifeexpectancy_over_energy") %>%
  map(get_cv_error, data = for_best_subset) %>%
  unlist()
cv.errors
options(scipen = 999)
which.min(cv.errors)
sort(coef(Best_Subset, 19))
```

```{r pca}

testDF_PCA <- PCA(testDF_imputed$completeObs, scale.unit = TRUE)

PCAshiny(testDF_PCA)

Investigate(testDF_PCA, file = "./PCA2018HighIncome.Rmd", document = "pdf_document",
            parallel = TRUE, Iselec = "contrib 58", nclust=7, ncp=4, ellipse=TRUE)
# Iselec = "contrib 120", nclust=8,
 
testDF_PCA_eig.val <- testDF_PCA$eig
barplot(testDF_PCA_eig.val[, 2],
        names.arg = 1:nrow(testDF_PCA_eig.val),
        main = "Variances Explained by PCs (%)",
        xlab = "Principal Components",
        ylab = "Percentage of variances",
        col ="steelblue")

testDF_PCA_var.cor <- data.frame(testDF_PCA$var$cor) %>% filter((Dim.1 > 0.8) | (Dim.2 > 0.8) | (Dim.3 > 0.8) | (Dim.4 > 0.8) | (Dim.5 > 0.8))

gr <- plot(testDF_PCA, choix='var', cex=0.5)
gr + theme(panel.grid.major = element_blank(),
   plot.title=element_text(size=14, color="blue"),
   axis.title = element_text(size=12, color="red")) + coord_cartesian(clip = "off", xlim = c(-2, 2))

testDF_PCA_summary <- list(Dim1 = apply(top_n(testDF_PCA_var.cor, 10, Dim.1)[,"Dim.1", drop=FALSE], 1, as.character, c), Dim2 = apply(top_n(testDF_PCA_var.cor, 10, Dim.2)[,"Dim.2", drop=FALSE], 1, as.character, c), Dim3 = apply(top_n(testDF_PCA_var.cor, 10, Dim.3)[,"Dim.3", drop=FALSE], 1, as.character, c), Dim4 = apply(top_n(testDF_PCA_var.cor, 10, Dim.4)[,"Dim.4", drop=FALSE], 1, as.character, c), Dim5 = apply(top_n(testDF_PCA_var.cor, 10, Dim.5)[,"Dim.5", drop=FALSE], 1, as.character, c))
testDF_PCA_summary

```

### Code for cleaning, merging, formatting imported data sets

Load initial data frame

```{r initial}
# staticPathWBGender <- "./Static/WBGender/"
# 
# DataSets <- list.files(staticPathWB)
# dfbase <- read.csv("./Static/base.csv")
# importedDF <- read.csv(paste(staticPathWB, DataSets[31], sep="")) %>% filter(Country.Code != "")
# tempList <- list(wbGenderAndValues, importedDF)
# wbJoined <- tempList %>% reduce(full_join, by=c('Country.Code', 'Year'))
# wbJoinedSorted <- wbJoined %>% arrange(Country.Code, Year)
# write.csv(wbJoinedSorted, "./Static/wbAndGender.csv")
```

Merging gender data

```{r cleandata}
# femaleparliament.csv <- femaleparliament.csv %>% rename_at('Value', ~'femaleparliament')
# femaleparliament <- femaleparliament.csv %>% select(c("Country.Code", "Year", "femaleparliament"))
# df_list <- list(femalemanager, femaleminister, femaleparliament)
# df_list_merged <- df_list %>% reduce(full_join, by=c('Country.Code', 'Year'))
# write.csv(df_list_merged, paste(staticPathWBGender, "merged.csv", sep=""), row.names=FALSE)
# genderDF <- read.csv(paste(staticPathWBGender, "merged.csv", sep=""))
# agriDF <- read.csv("./Static/WB/pivoted/agriculture.csv") %>% filter(Country.Code != "")
# formattedAgriDF <- formatWBYears(agriDF) %>% rename_at('value', ~"agriculture")
# newdflist <- list(genderDF, formattedAgriDF)
# newBaseDF <- newdflist %>% reduce(right_join, by=c('Country.Code', 'Year')) %>% select(c("Country.Name", "Country.Code", "Year", "agriculture", "femalemanager", "femaleminister", "femaleparliament"))
# write.csv(newBaseDF, "./Static/base.csv", row.names = FALSE)

```

Adding variables from various datasets to the main base data frame

```{r addvars}
#withWID <- read.csv("./Static/withWID.csv")
#withIncomeGroups <- read.csv("./withIncomeGroups.csv")
#incomegroups <- read.csv("./Static/Manual/incomegroup.csv", sep = ";")
#incomegroupslist <- list(withWID, incomegroups)
#withIncomeGroups <- incomegroupslist %>% reduce(left_join, by=c('Country.Code')) %>% select(!"Country.Name.y") %>% #rename(Country.Name = Country.Name.x)
#outcomes <- read.csv("./Static/Manual/dependentvars/outcomes_full.csv", sep=";")
# outcomes_selected <- outcomes %>% select(!c("democraticquality", "equality", "employment"))
#outcomeslist <- list(withIncomeGroups, outcomes_selected)
#withOutcomes <- outcomeslist %>% reduce(left_join, by=c('Country.Code', 'Year')) %>% select(!"Country.Name.y") %>% rename(Country.Name = Country.Name.x)

# wbGender <- read.csv("./Static/wbAndGender.csv")
# values <- read.csv("./Static/Manual/processed/WVS/values.csv")
# values_df <- values %>% select(c("S020", "COUNTRY_ALPHA", "A006", "F050", "F202", "F028B", "A040", "A103", "A106B", "A105", "A104", "A106C", "F114B", "F117", "F116",  "F114D", "F199", "E069_07", "E069_11", "E069_08", "E069_12", "E069_17", "H006_05", "H006_04", "H006_03", "H006_02", "H006_06")) %>% rename(Year=S020, Country.Code=COUNTRY_ALPHA, ReligionImportant=A006, BelieveGod=F050,ReligionOverScience=F202,PrayOften=F028B,ChildFaith=A040,EnvOrgMember=A103,ConsumOrgMember=A106B,CharityOrgMember=A105,ProfOrgMember=A104,SelfHelpOrgMember=A106C,StealProp=F114B,AcceptBribe=F117,TaxCheat=F116,Violence=F114D,BeatWife=F199,ConfParliament=E069_07,ConfGov=E069_11,ConfCivilService=E069_08,ConfParties=E069_12,ConfCourts=E069_17,WorryCivilWar=H006_05,WorryTerrorist=H006_04,WorryWar=H006_03,WorryEduc=H006_02,WorryGovPrivacy=H006_06)
# values_df_agg <- values_df %>% group_by(Year, Country.Code) %>% summarise_at(vars(A001:X051), mean, na.rm = TRUE)
# write.csv(values_df_agg,"./Static/Manual/processed/WVS/values_df_agg.csv")
# values_df_final <- values_df_aggregated %>% select(-c("ReligionImportant", "ReligionOverScience", "PrayOften"))
# 
# wbGenderAndValuesList <- list(wbGender, values_df_final)
# wbGenderAndValues <- wbGenderAndValuesList %>% reduce(full_join, by=c('Country.Code', 'Year'))
# 
# wbJoinedSorted <- wbGenderAndValues %>% arrange(Country.Code, Year)
# write.csv(wbJoinedSorted, "./Static/wbGenderAndValues.csv")

# eci <- read.csv("./Static/Manual/ecirank/rankings.csv")
# eci_formatted <- eci %>% select(year, sitc_eci, code) %>% rename(Year=year, ecirank=sitc_eci, Country.Code=code)
# wbGenderValuesGovExp <- read.csv("./Static/wbGenderValuesAndGovExp.csv")
# write.csv(wbJoinedSorted, "./Static/wbGenderValuesAndGovExp.csv")

# homicide <- read.csv("./Static/Manual/homicide.csv")
# homicide_formatted <- homicide %>% select(!"Entity") %>% rename(Country.Code=Code, homicide=	
# Share.of.total.deaths...Both.Sexes...All.ages)
# write.csv(wbJoinedSorted, "./Static/wbGenderValuesECIHomicide.csv")

#patents_formatted <- readAndPivotWB("./Static/Manual/patents_fmt_withcodes.csv", "X.*", ";") %>%  #rename(Country.Code=Origin..Code., patents=value)
#patents_withyears <-  formatWBYears(patents_formatted) %>% select(Country.Code, Year, patents)

# gendergap <- read.csv("./Static/Manual/gendergap.csv")
# gendergap_formatted <- gendergap %>% select(!Entity) %>% rename(Country.Code=Code, gendergap=Gender.wage.gap....)

# gini <- read.csv("./Static/WB/pivoted/formatted/gini.csv")

# concentration <- readAndPivotWB("./Static/Manual/concentration/concentration.csv", "X.*", sep=";")
# concentration_formatted <- concentration %>% select(c(Country.Name, year, value))
# concentration_withyears <- formatWBYears(concentration_formatted) %>% select(!"year") %>% rename(concentration=value)

# ethnic <- read.csv("./Static/Manual/ethnic/HIEF_data.csv") %>% rename(Country.Name=Country, ethnic=EFindex)

# divorce <- read.csv("./Static/Manual/divorces.csv")
# divorce_formatted <- divorce %>% select(!Entity) %>% rename(Country.Code=Code,divorce=Crude.divorce.rate..per.1.000.inhabitants.)

# unvotes <- read.csv("./Static/Manual/unvotes/IdealpointestimatesAll_Jun2022.csv")
# unvotes_formatted <- unvotes %>% select(iso3c, session, IdealPointAll) %>% rename(Country.Code=iso3c, Year=session,unvotes=IdealPointAll)
# unvotes_formatted$Year <- unvotes_formatted$Year + 1945

# ideology <- read.csv("./Static/Manual/leaderideology.csv")
# ideology_formatted <- ideology %>% select(c(country_name, year, hog_left)) %>% rename(Country.Name=country_name, Year=year, ideology=hog_left)

# informal <- readAndPivotWB("./Static/Manual/informal.csv", "X.*")
# informal_formatted <- formatWBYears(informal) %>% select(!year) %>% rename(Country.Name=Economy, Country.Code=Code, informal=value)
# 
# wbGenderValuesECIHomicidePatentGGapGiniConcEthnicDivorceUNIdeologyInformalList <- list(wbGenderValuesECIHomicidePatentGGapGiniConcEthnicDivorceUNIdeology, informal_formatted)
# wbGenderValuesECIHomicidePatentGGapGiniConcEthnicDivorceUNIdeologyInformal <- wbGenderValuesECIHomicidePatentGGapGiniConcEthnicDivorceUNIdeologyInformalList %>% reduce(left_join, by=c('Country.Code', 'Year')) %>% select(!Country.Name.y) %>% rename(Country.Name=Country.Name.x)

# population <- read.csv("./Static/Manual/population.csv")
# population_countries <- population %>% filter(ISO3_code != "") %>% select(ISO3_code, Location, TPopulation1Jan, Time) %>% filter(Time < 2022) %>% rename(Country.Code=ISO3_code, Country.Name=Location, population=TPopulation1Jan, Year=Time)
# population_countries$population <- population_countries$population * 1000
# population_with100k <- population_countries %>% mutate(pop100k=(population/100000))
# 
# prison <- read.csv("./Static/Manual/prison/prison_nationals.csv")
# prison_formatted <- prison %>% select(Iso3_code, Country, Year, VALUE) %>% rename(Country.Code=Iso3_code, Country.Name=Country, prisontotal=VALUE)
# prison_formatted$Country.Code <- gsub("GBR_E_W", "GBR", prison_formatted$Country.Code)
# prison_pop_list <- list(prison_formatted, population_with100k)
# prison_pop <- prison_pop_list %>% reduce(left_join, by=c('Country.Code', 'Year')) %>% select(!Country.Name.x) %>% rename(Country.Name=Country.Name.y) %>% mutate(prison = prisontotal / pop100k) %>% select(!c(prisontotal, population, pop100k))
# 
# withPrisonList <- list(withInformal, prison_pop)
# withPrison <- withPrisonList %>% reduce(left_join, by=c('Country.Code', 'Year'))  %>% select(!Country.Name.y) %>% rename(Country.Name=Country.Name.x)
# write.csv(withPrison, "./Static/withPrison.csv")

# Add WID data

# wealth <- read.csv("./Static/Manual/WID/wealth/wealth_formatted.csv", sep=";")
# femaleincome <- read.csv("./Static/Manual/WID/femaleincome/femaleincome_formatted.csv", sep=";")
# femaleincome[femaleincome == 0] <- NA
# onepcwealth <- read.csv("./Static/Manual/WID/onepcwealth/onepcwealth_formatted.csv", sep=";")
# onepcincome <- read.csv("./Static/Manual/WID/onepcincome/onepcincome_formatted.csv", sep=";")
# wealthincome <- read.csv("./Static/Manual/WID/wealthincome/wealthincome_formatted.csv", sep=";")

## CHECK WHY DUPLICATES ARE CREATED HERE IN LEFT JOIN

# prisonWealthList <- list(withPrison, wealth)
# withPrisonWealth <- prisonWealthList %>% reduce(left_join, by=c('Country.Name', 'Year')) %>% rename(wealth=Wealth)
# withPrisonWealthNoDupes <- withPrisonWealth[!duplicated(withPrisonWealth[c("Country.Name","Year")]),]
# 
# prisonWealthFemaleIncomeList <- list(withPrisonWealthNoDupes, femaleincome)
# withPrisonWealthFemaleIncome <- prisonWealthFemaleIncomeList %>% reduce(left_join, by=c('Country.Name', 'Year'))
# 
# withOnePcWealthList <- list(withPrisonWealthFemaleIncome, onepcwealth)
# withOnePcWealth <- withOnePcWealthList %>% reduce(left_join, by=c('Country.Name', 'Year'))
# withOnePcWealthNoDupes <- withOnePcWealth[!duplicated(withOnePcWealth[c("Country.Name","Year")]),]
# 
# withOnePcIncomeList <- list(withOnePcWealthNoDupes, onepcincome)
# withOnePcIncome <- withOnePcIncomeList %>% reduce(left_join, by=c('Country.Name', 'Year'))
# withOnePcIncomeNoDupes <- withOnePcIncome[!duplicated(withOnePcIncome[c("Country.Name","Year")]),]
# 
# withWealthIncomeList <- list(withOnePcIncome, wealthincome)
# withWealthIncome <- withWealthIncomeList %>% reduce(left_join, by=c('Country.Name', 'Year'))
# withWealthIncomeNoDupes <- withWealthIncome[!duplicated(withWealthIncome[c("Country.Name","Year")]),]
```