---
title: "Socio-economic conditions reproduction"
author: "Val"
date: "7/29/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("utils/functions.R")
library(tidyr)
library(dplyr)
library(tidyverse)
```

### Loading data

Load and prepare data for need satisfaction
```{r load_data_needsatisfaction}
ns_wdi_datasets <- c("undernourishment", "water", "sanitation", "povertygap")
for (dataset in ns_wdi_datasets) {assign(dataset, initializeWBDataset(dataset, "need_satisfaction/", ".csv", "X.*", 2002, 2013))}
lifeexp <- read.csv("need_satisfaction/haleowid.csv") %>% select(Country.Name=Entity, Country.Code=Code, Year, lifeexp=Healthy.Life.Expectancy..IHME.) %>% filter(Year %in% (2002:2013), Country.Code != "")
### Leaving out education for now as data is only for each 5 years until 2005
#education <- read.csv("hdi_education_index.csv") %>% select(Country.Name=country, Country.Code=country_code, Year=year, education=value) %>% filter(Year %in% (1990:2013), Country.Code != "")
```

Load and prepare data for provisioning factors
```{r load_data_provisioning}
ps_wdi_wgi_datasets <- c("electricity", "cleanfuel", "transportquality", "urbanlevel", "goveffectiveness", "outofpocket", "voice", "gini", "resourcerents", "fdi", "trade")
for (dataset in ps_wdi_wgi_datasets) {assign(dataset, initializeWBDataset(dataset, "provisioning_factors/", ".csv", "X.*", 2002, 2013))}
gdppercap <- initializeWBDataset("gdppercap", "provisioning_factors/", ".csv", "X.*", 2001, 2014)
```

Calculate gdp growth from gdp per capita (PPP) using lag of variable
```{r gdp_growth}
gdpgrowth <- gdppercap %>% group_by(Country.Name) %>% arrange(Year) %>% mutate(gdpgrowth = ((gdppercap - lag(gdppercap)) / (Year - lag(Year)))/lag(gdppercap) * 100) %>% ungroup() %>% select(-gdppercap) %>% arrange(Country.Name) %>% filter(Year %in% (2002:2013))
```

Reverse gini and outofpocket variables
```{r reverse_gini}
equality <- gini %>% mutate(equality=100-gini) %>% select(-gini)
healthcov <- outofpocket %>% mutate(healthcov=100-outofpocket) %>% select(-outofpocket)
```

Re-scale WGI variables on a scale of 1 to 6 (original scale is -2.5 to 2.5)
```{r rescale_wgi}
goveffectiveness_rescaled <- goveffectiveness %>% mutate(goveffectiveness = ((6 - 1) / (2.5 - (-2.5))) * (goveffectiveness - (-2.5)) + 1)
voice_rescaled <- voice %>% mutate(voice = ((6 - 1) / (2.5 - (-2.5))) * (voice - (-2.5)) + 1)
```

Re-scale undernourishment on a scale from 0 to 100 (original scale is not specified in the data)
```{r rescale_undernourishment}
undernourishment_rescaled <- undernourishment %>% mutate(undernourishment = (100 / (max(undernourishment, na.rm = TRUE) - min(undernourishment, na.rm = TRUE))) * (undernourishment - min(undernourishment, na.rm = TRUE)))
```

Reverse undernourishment and povertygap
```{r}
nourishment <- undernourishment_rescaled %>% mutate(nourishment=100-undernourishment) %>% select(-undernourishment)
nopoverty <- povertygap %>% mutate(nopoverty=100-povertygap) %>% select(-povertygap)
```

Join each table into data frames for need satisfaction and provisioning factors
```{r assemble}
ns_vars <- c("lifeexp", "nourishment", "water", "sanitation", "nopoverty")
ps_vars <- c("electricity", "cleanfuel", "transportquality", "urbanlevel", "goveffectiveness_rescaled", "healthcov", "voice_rescaled", "equality", "gdpgrowth", "resourcerents", "fdi", "trade")
ns_list <- mget(ns_vars)
ns_all <- ns_list %>% reduce(left_join, by=c('Country.Name', 'Country.Code', 'Year'))
ps_list <- mget(ps_vars)
ps_all <- ps_list %>% reduce(left_join, by=c('Country.Name', 'Country.Code', 'Year'))
```

Load and prepare data for energy use. Filter to only keep countries we have need satisfaction data for
```{r load_data_energy_use}
energyuse <- initializeWBDataset("energyuse", "energy_use/", ".csv", "X.*", 2002, 2013)
enu_list <- list(ns_all, energyuse)
filtered_energyuse <-  enu_list %>% reduce(left_join, by=c('Country.Name', 'Country.Code', 'Year'))
```

Clean-up initially imported data frames
```{r initial_cleanup}
unused_vars <- c("gdppercap", "gini", "goveffectiveness", "outofpocket", "povertygap", "undernourishment", "undernourishment_rescaled")
rm(list=c(ns_vars, ps_vars, unused_vars))
```

Prepare data frames to be used with original analysis
```{r prep_original}
ns_p <- ns_all %>% select(4:length(ns_all))
ps_p <- ps_all %>% select(4:length(ps_all))
enu_os4m <- select(filtered_energyuse, length(filtered_energyuse))[[1]]
```

Prepare utility objects to be used in analysis
```{r prep_utility_objects}
a <- list()
ll <- list()
nc <- list(hs = length(ps_p$transportquality)) # Replace with the appropriate value
st <- list(ns_m_sd = c(), ns_m_means = c()) # Modify as needed
r <- list()
r_bvr <- list()
# Create nv object with the number of variables (columns) in ns_p and ps_p
nv <- list(ns_all = ncol(ns_p), ps_all = ncol(ps_p), ns_m=ncol(ns_p))
# Create tf object with the desired transformations and saturation values
tf <- list(
  ns_tf_use = c("sat", "sat", "sat", "sat", "sat"), # Transformation types for each variable
  ns_m_tf_use = c("sat", "sat", "sat", "sat", "sat"),
  enu_tf_use = c("log"),
  ps_tf_use = c("sat", "sat", "lin", "lin", "lin", "lin", "sat", "sat", "lin", "log", "log", "lin"),
  ns_sat_val = c(77, 100.3, 100.7, 100.7, 100.3), # Saturation values (only used for "sat" transformation)
  ps_sat_val = c(100.7, 100.7, 0, 0, 0, 0, 1.93, 84.6, 0, 0, 0, 0),
  ns_m_offsets = c()
)
# This is true if in this variable bigger values are better
g <- list(
  ns_more_is_better = c(TRUE, TRUE, TRUE, TRUE, TRUE), 
  ns_m_sign_for_sat_retrafo = c(), 
  ns_m_more_is_better = c(TRUE, TRUE, TRUE, TRUE, TRUE)
)
```

### BEGIN ORIGINAL ANALYSIS

Conduct transformations on NS variables
```{r ns_transformations}
### Need satisfaction variables
### NS variable transformations (can be simplified as I used sat-transformations on all NS variables in the end)

ns_tf <- ns_p

for ( nn in 1:nv$ns_all ){
  
  if ( tf$ns_tf_use[[ nn ]] == "log" ) {    ns_tf[ , nn ]  <-  log ( ns_p[ , nn ] ) }
  
  if ( ( tf$ns_tf_use[[ nn ]] == "sat" ) & ( g$ns_more_is_better[nn]  )) {  ns_tf[ , nn ]  <-  log ( tf$ns_sat_val[[nn]] - ns_p[ , nn ] ) }
  if ( ( tf$ns_tf_use[[ nn ]] == "sat" ) & ( ! g$ns_more_is_better[nn] )) {  ns_tf[ , nn ]  <-  log ( ns_p[ , nn ] - tf$ns_sat_val[[nn]] ) }
  
  # g$ns_more_is_better indicates whether the NS variable is one where higher values are better (e.g. life expectancy) or where lower values are better (e.g. child mortality)
  # if neither "log" nor "sat", ns_tf[,nn] will remain equal to ns_p[,nn], i.e. identity trafo
}
```

Conduct transformations on PS variables. This produces NaNs so remove them/replace with NAs
```{r ps_transformations}
ps_tf <- ps_p

for ( pp in 1:nv$ps_all ){
  ### PS variable transformations
  if ( tf$ps_tf_use[ pp ] == "lin" ) {   ps_tf[ , pp ]    <-   ps_p [ , pp ]      }
  
  if ( tf$ps_tf_use[ pp ] == "log" ) {   ps_tf[ , pp ]    <-   log ( ps_p [ , pp ] )     }
  
  if ( tf$ps_tf_use[ pp ] == "sat" ) {   ps_tf[ , pp ]    <-   log ( tf$ps_sat_val[ pp ]  -  ps_p [ , pp ] )     }
  # maximum-type only 
}
ps_tf[ps_tf == "NaN"] <- NA
```

There is only one energy use variable. Apply log transformation to it
```{r enu_transformations}
enu_m <- log(enu_os4m)
```

Conduct bivariate regressions. I assumed that we start with transformed data here
```{r bivariate}
#### --- bivariate regressions --- ####
### fs = fit space (= transformed versions of variables, used for regressions)
### os = original space (= untransformed variables)

ns_m <- ns_tf
ns_os4m <- ns_p
# Get the number of columns from the length of nv$ns_m
#num_columns <- nv$ns_m
# Initialize the number of rows
#num_rows <- length(ll$ns_pred_os)
# Initialize the matrix within the list
#r_bvr$NSpred_ENUonly_sortENU <- matrix(NA, nrow = num_rows, ncol = num_columns)


for ( nn in 1:nv$ns_m ){
  
  a$ind_sortENU   <-  sort( enu_os4m,  index.return = TRUE )
  
  a$enu_p75_os  <-  sort( enu_os4m)[0.75 * nc$hs ]
  
  a$enu_p75_fs  <-  sort( enu_m)[0.75 * nc$hs ]
  
  ll$mo <-  lm ( ns_m[ , nn ] ~ enu_m )
  
  ll$a  <- ll$mo$coefficients[1]
  ll$b  <- ll$mo$coefficients[2]
  
  if ( tf$ns_m_tf_use[[ nn ]] == "lin"  ){
    
    ll$ns_pred_os  <-    ( ll$mo$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  -  tf$ns_m_offsets[[ nn ]]  
    
    ll$ns_pred_os_for_enu_p75  <-  ( ( ll$a + ll$b * a$enu_p75_fs ) * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  - tf$ns_m_offsets[[ nn ]]
    
  }
  
  if ( tf$ns_m_tf_use[[ nn ]] == "log"  ){
    
    ll$ns_pred_os  <-   exp ( ( ll$mo$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) -  tf$ns_m_offsets[[ nn ]]  
    
    ll$ns_pred_os_for_enu_p75  <- exp ( ( ( ll$a + ll$b * a$enu_p75_fs ) * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]]
    
  }
  
  if ( tf$ns_m_tf_use[[ nn ]] == "sat"  ){
    
    ll$ns_pred_os  <-  tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]  +  g$ns_m_sign_for_sat_retrafo[ nn ]  *    
      exp ( ( ll$mo$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )    
    
    ll$ns_pred_os_for_enu_p75  <-  tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]  +  g$ns_m_sign_for_sat_retrafo[ nn ]  *    
      exp ( ( ( ll$a + ll$b * a$enu_p75_fs ) * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )  
  }
  
  r$ns_enu_r2_adj[ nn  ]  <- summary( ll$mo  )$adj.r.squared
  
  r$r_enu_p75_minus_med_to_med[ nn  ]  <-  (  a$enu_p75_os  - median( enu_os4m) ) / median( enu_os4m )
  r$r_enu_p75_minus_med_to_med_frommin[ nn  ]  <-  (  a$enu_p75_os  - median( enu_os4m) ) / ( median( enu_os4m ) - min(enu_os4m) )
  
  if( g$ns_m_more_is_better[ nn ] ){ 
    r$r_ns_pred_p75_minus_med_to_med[ nn  ]  <-  ( ll$ns_pred_os_for_enu_p75   - median( ll$ns_pred_os ) ) / median( ll$ns_pred_os )
    r$r_ns_pred_p75_minus_med_to_med_frommin [ nn ]  <-  ( ll$ns_pred_os_for_enu_p75   - median( ll$ns_pred_os ) ) / ( median( ll$ns_pred_os ) - min ( ns_os4m[ , nn ] ) )
  }
  if( ! g$ns_m_more_is_better[ nn ] ){   # not really needed anymore
    r$r_ns_pred_p75_minus_med_to_med[ nn ]  <- ( ( 100 - ll$ns_pred_os_for_enu_p75 ) - (100 - median( ll$ns_pred_os )) ) / ( 100 -  median( ll$ns_pred_os ) )
  }
  # r_bvr$NSpred_ENUonly_sortENU[  , nn ] <-  ll$ns_pred_os[ a$ind_sortENU$ix ]
}  
```

Bivariate regression plots
```{r bivariate_plots}
### prepare bi-variate plots

for ( nn in 1:nv$ns_m ){
  a$ind_sortENU   <-  sort( enu_os4m,  index.return = TRUE )
  
  ll$mo <-  lm ( ns_m[ , nn ] ~ enu_m)
  
  ll$a  <- ll$mo$coefficients[1]
  ll$b  <- ll$mo$coefficients[2]
  
  if ( tf$ns_m_tf_use[[ nn ]] == "lin"  ){
    ll$ns_pred_os  <-    ( ll$mo$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  -  tf$ns_m_offsets[[ nn ]]  
  }
  
  if ( tf$ns_m_tf_use[[ nn ]] == "log"  ){
    ll$ns_pred_os  <-   exp ( ( ll$mo$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) -  tf$ns_m_offsets[[ nn ]]  
  }
  
  if ( tf$ns_m_tf_use[[ nn ]] == "sat"  ){
    ll$ns_pred_os  <-  tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]  +  g$ns_m_sign_for_sat_retrafo[ nn ]  *    
      exp ( ( ll$mo$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )    
  }
}

r_enu_in_perc  <- r$r_enu_p75_minus_med_to_med[] * 100
r_enu_in_perc_frommin  <- r$r_enu_p75_minus_med_to_med_frommin[] * 100

r_ns_in_perc <- r$r_ns_pred_p75_minus_med_to_med * 100
r_ns_in_perc_frommin <- r$r_ns_pred_p75_minus_med_to_med_frommin * 100

ns_response  <- r$r_ns_pred_p75_minus_med_to_med / r$r_enu_p75_minus_med_to_med
```

Conduct moderation analysis

```{r moderation}

##### moderation analysis ######

g$ns_m_more_is_better_as_sign <-  0 * g$ns_m_more_is_better 
g$ns_m_more_is_better_as_sign [ g$ns_m_more_is_better ]   <-   1
g$ns_m_more_is_better_as_sign [ ! g$ns_m_more_is_better ] <-  -1

a$ns_floor    <- c( min( ns_os4m$hale ) , min(ns_os4m$fooddef) , min(ns_os4m$water) ,
                    min(ns_os4m$sani), min(ns_os4m$edubas) ,   min(ns_os4m$povgap320)  ) 
a$ns_ceiling  <- c( max( ns_os4m$hale ) ,max(ns_os4m$fooddef) , max(ns_os4m$water) ,
                    max(ns_os4m$sani), max(ns_os4m$edubas) ,   max(ns_os4m$povgap320) ) 

for ( nn in 1:nv$ns_m) {
  for ( pp in 1:nv$ps_u ){
    
    if ( ! tf$ps_u_tf_use[ pp ] == "sat"    ) { g$sign_normaliser_imprNS_dNS_dPS_u [ nn , pp ]  <-   g$sign_normaliser_imprNS_for_effects_on_ns_m[ nn ] }
    if ( tf$ps_u_tf_use[ pp ] == "sat"    )  { g$sign_normaliser_imprNS_dNS_dPS_u [ nn , pp ]   <-   ( - 1 )* g$sign_normaliser_imprNS_for_effects_on_ns_m[ nn ] }
  }
}
```

What is this?

```{r megaloop}
###################### START MEGA-LOOP ###############################

ll$nrow  <-  0
for ( nn in 1 : nv$ns_m ) {
  
  ll$ns  <-  ns_m[ , nn ]
  ll$ns_os   <-  ns_os4m[ , nn ]
  
  ll$ns_os_range  <-  abs(  a$ns_ceiling[nn] - a$ns_floor[nn] )
  
  ## partly unnecessary, remainder of previous version with different energy variables 
  ll$enu  <-  enu_m
  ll$enu_os   <-   enu_os4m
  ll$enu_sortENU      <-  sort ( ll$enu )
  ll$ind_sortENU      <-  sort ( ll$enu  , index.return = TRUE )$ix
  ll$enu_os_sortENU   <-   ll$enu_os[ ll$ind_sortENU ]
  ##
  
  for ( pp in 1 : nv$ps_u ) {

    ll$nrow <-  ll$nrow + 1
    
    ll$ps     <-  ps_u[ , pp ]
    ll$ps_os  <-  ps_os_u[ , pp ]
    
    ll$ps_sortPS    <-   sort ( ll$ps )
    ll$ind_sortPS   <-   sort ( ll$ps , index.return = TRUE )$ix
    
    ll$ps_os_sortPS    <-   sort ( ll$ps_os )     ## note this is NOT necessarily the same as sortPS because for sat trafo, the order is reversed in fs vs os
    ll$ind_sortPSos   <-   sort ( ll$ps_os , index.return = TRUE )$ix    ## note this is NOT necessarily the same as sortPS because for sat trafo, the order is reversed in fs vs os
    
    ll$enu_sortPS         <-   ll$enu[ ll$ind_sortPS ]
    ll$enu_os_sortPS      <-   ll$enu_os[ ll$ind_sortPS ]
    ll$ps_os_sortPS       <-   ll$ps_os[ ll$ind_sortPS ]
    
    ll$ps_sortENU      <-   ll$ps [ ll$ind_sortENU ]
    ll$ps_os_sortENU   <-   ll$ps_os [ ll$ind_sortENU ]
    
    ll$ns_sortENU     <-   ll$ns [ ll$ind_sortENU ]
    ll$ns_os_sortENU  <-   ll$ns [ ll$ind_sortENU ]
    
    
    ### ---- calculate ps values at given percentiles (for constrained prediction) ----- ###
    
    ll$ps_p50  <-  median ( ll$ps_sortPS )
    
    ll$ps_p100  <-  ll$ps_sortPS[ nc$hs ]
    ll$ps_p1    <-  ll$ps_sortPS[ 1 ]
    
    ll$ps_p95  <-  ll$ps_sortPS[ 1 + round ( 0.95 * (nc$hs -1 ) )  ]
    ll$ps_p90  <-  ll$ps_sortPS[ 1 + round ( 0.9 * (nc$hs -1 ) )  ]
    ll$ps_p80  <-  ll$ps_sortPS[ 1 + round ( 0.8 * (nc$hs -1 ) )  ]
    ll$ps_p75  <-  ll$ps_sortPS[ 1 + round ( 0.75 * (nc$hs -1 ) )  ]
    ll$ps_p70  <-  ll$ps_sortPS[ 1 + round ( 0.7 * (nc$hs -1 ) )  ]
    ll$ps_p30  <-  ll$ps_sortPS[ 1 + round ( 0.3 * (nc$hs -1 ) )  ]
    ll$ps_p25  <-  ll$ps_sortPS[ 1 + round ( 0.25 * (nc$hs -1 ) )  ]
    ll$ps_p20  <-  ll$ps_sortPS[ 1 + round ( 0.2 * (nc$hs -1 ) )  ]
    ll$ps_p10  <-  ll$ps_sortPS[ 1 + round ( 0.1 * (nc$hs -1 ) )  ]
    ll$ps_p5   <-  ll$ps_sortPS[ 1 + round ( 0.05 * (nc$hs -1 ) )  ]
    
    ll$ps_os_p95  <-  ll$ps_os_sortPS[ 1 + round ( 0.95 * (nc$hs -1 ) ) ]
    ll$ps_os_p90  <-  ll$ps_os_sortPS[ 1 + round ( 0.9 * (nc$hs -1 ) ) ]
    ll$ps_os_p80  <-  ll$ps_os_sortPS[ 1 + round ( 0.8 * (nc$hs -1 ) )  ]
    ll$ps_os_p75  <-  ll$ps_os_sortPS[ 1 + round ( 0.75 * (nc$hs -1 ) )  ]
    ll$ps_os_p70  <-  ll$ps_os_sortPS[ 1 + round ( 0.7 * (nc$hs -1 ) )  ]
    ll$ps_os_p30  <-  ll$ps_os_sortPS[ 1 + round ( 0.3 * (nc$hs -1 ) )  ]
    ll$ps_os_p25  <-  ll$ps_os_sortPS[ 1 + round ( 0.25 * (nc$hs -1 ) )  ]
    ll$ps_os_p20  <-  ll$ps_os_sortPS[ 1 + round ( 0.2 * (nc$hs -1 ) )  ]
    ll$ps_os_p10  <-  ll$ps_os_sortPS[ 1 + round ( 0.1 * (nc$hs -1 ) )  ]
    ll$ps_os_p5   <-  ll$ps_os_sortPS[ 1 + round ( 0.05 * (nc$hs -1 ) )  ]
    
    
    
    if ( ! tf$ps_u_tf_use[ pp ] == "sat"  ) {   
      
      ll$ps_fs_p75os   <-   ll$ps_p75               # these are the PS values in fitspace (fs) = transformed, at the percentiles of the os variables (i.e. sign-sensitive)
      ll$ps_fs_p80os   <-   ll$ps_p80               # these are the PS values in fitspace (fs) = transformed, at the percentiles of the os variables (i.e. sign-sensitive)
      ll$ps_fs_p90os   <-   ll$ps_p90 
      ll$ps_fs_p95os   <-   ll$ps_p95 
      ll$ps_fs_p100os  <-   ll$ps_p100 
      
      ll$ps_fs_p25os  <-   ll$ps_p25 
      ll$ps_fs_p20os  <-   ll$ps_p20 
      ll$ps_fs_p10os  <-   ll$ps_p10 
      ll$ps_fs_p5os   <-   ll$ps_p5 
      ll$ps_fs_p1os   <-   ll$ps_p1   }
    
    
    if ( tf$ps_u_tf_use[ pp ] == "sat"  ) {   
      
      ll$ps_fs_p75os   <-   ll$ps_p25               # these are the PS values in fitspace (fs) = transformed, at the percentiles of the os variables (i.e. sign-sensitive)
      ll$ps_fs_p80os   <-   ll$ps_p20               # these are the PS values in fitspace (fs) = transformed, at the percentiles of the os variables (i.e. sign-sensitive)
      ll$ps_fs_p90os   <-   ll$ps_p10 
      ll$ps_fs_p95os   <-   ll$ps_p5 
      ll$ps_fs_p100os  <-   ll$ps_p1 
      
      ll$ps_fs_p25os   <-   ll$ps_p75               # these are the PS values in fitspace (fs) = transformed, at the percentiles of the os variables (i.e. sign-sensitive)
      ll$ps_fs_p20os   <-   ll$ps_p80
      ll$ps_fs_p10os   <-   ll$ps_p90  
      ll$ps_fs_p5os    <-   ll$ps_p95   
      ll$ps_fs_p1os    <-   ll$ps_p100   }
    
    ### ---- bivariate models --- ###
    
    mo1e  <-   lm( ll$ns  ~  ll$enu )   # mo1e = model object, 1 predictor, energy as predictor
    mo1p  <-   lm( ll$ns  ~  ll$ps  )   # mo1p = model object, 1 predictor, , PS as predictor
    
    mo1e_rob  <- lm_robust( ll$ns  ~  ll$enu , se_type = sw$HC)
    mo1p_rob  <- lm_robust( ll$ns  ~  ll$ps  , se_type = sw$HC)
    
    
    mo1e$b1_enu_gate    <-  (summary(mo1e_rob))$coefficients[2,4]   <   ch$th_p_b_bivar
    mo1p$b1_ps_gate     <-  (summary(mo1p_rob))$coefficients[2,4]   <   ch$th_p_b_bivar
    
    # ks test
    r_bvr_ks$kstest[ nn ] <-  ks.test ( sort( mo1e$residuals ) , "pnorm",  0 , sd (  mo1e$residuals  ) )$p.value
    
    
    ####################################################################
    
    ## multiplicative 2-predictor OLS regression (with interaction)
    mo2i  <-   lm( ll$ns  ~  ll$enu * ll$ps )
    mo2i_rob  <-   lm_robust( ll$ns  ~  ll$enu * ll$ps , se_type = sw$HC )
    
    # ks test
    r_mod$kstest[ pp , nn ] <-  ks.test ( sort( mo2i$residuals ) , "pnorm",  0 , sd (  mo2i$residuals  ) )$p.value
    
    # extracting model coefficients
    mo2i$a       <-  mo2i$coefficients[1]
    mo2i$b1_enu  <-  mo2i$coefficients[2]
    mo2i$b2_ps   <-  mo2i$coefficients[3]
    mo2i$b3_int  <-  mo2i$coefficients[4]
    
    
    # calculate variance-covariance matrix (and extract terms)
    mo2i_rob$varcov  <-   vcovHC ( mo2i , type = sw$HC)
    
    mo2i_rob$var_b1_enu       <- mo2i_rob$varcov[2,2]
    mo2i_rob$var_b2_ps        <- mo2i_rob$varcov[3,3]
    mo2i_rob$var_b3_int       <- mo2i_rob$varcov[4,4]
    mo2i_rob$cov_b1ENU_b3INT  <- mo2i_rob$varcov[4,2]
    mo2i_rob$cov_b2PS_b3INT   <- mo2i_rob$varcov[4,3]
    mo2i$ps_signi_b2b3joint  <-  (wald.test(b = coef(mo2i_rob), Sigma = vcovHC( mo2i , type = sw$HC), Terms = 3:4))$result$chi2[[3]] # tests joint significance of b2(PS) and b3 (ENU*PS).
    
    # calculate standard errors for the marginal effects of ENU and PS, respectively
    
    mo2i$marg_eff_enu_sortPS  <-   mo2i$b1_enu  +  ( mo2i$b3_int * ll$ps_sortPS )  # this is dNS/dENU as a function of PS, sorted by PS
    
    mo2i$std_err_marg_eff_enu_sortPS  <-   sqrt ( mo2i_rob$var_b1_enu  +  ( ll$ps_sortPS ^2 ) * mo2i_rob$var_b3_int  +
                                                    2 * ll$ps_sortPS * mo2i_rob$cov_b1ENU_b3INT )
    
    
    mo2i$marg_eff_ps_sortENU  <-   mo2i$b2_ps  +  ( mo2i$b3_int * ll$enu_sortENU )   # this is dNS/dPS as a function of ENU, sorted by ENU
    
    mo2i$std_err_marg_eff_ps_sortENU  <-   sqrt ( mo2i_rob$var_b2_ps + ( ll$enu_sortENU ^2 ) * mo2i_rob$var_b3_int  +
                                                    2 * ll$enu_sortENU * mo2i_rob$cov_b2PS_b3INT )
    
    
    
    r_mod_test$sigma_dNS_dENU_sqrt_arg[ , nn , pp ]  <- mo2i_rob$var_b1_enu  +  ( ll$ps_sortPS ^2 ) * mo2i_rob$var_b3_int  +
      2 * ll$ps_sortPS * mo2i_rob$cov_b1ENU_b3INT
    
    r_mod_test$sigma_dNS_dPS_sqrt_arg[ , nn , pp ]  <- mo2i_rob$var_b2_ps + ( ll$enu_sortENU ^2 ) * mo2i_rob$var_b3_int  +
      2 * ll$enu_sortENU * mo2i_rob$cov_b2PS_b3INT
    
    r_mod_test$sigma_dNS_dENU[ , nn , pp ]   <- mo2i$std_err_marg_eff_enu_sortPS
    
    r_mod_test$sigma_dNS_dPS[ , nn , pp ]   <- mo2i$std_err_marg_eff_ps_sortENU 
    
    
    
    # calculate 95% confidence intervals, assuming normal distribution (z = 1.96 for 95% confidence intervals) ; zscore now set in ch$zscore_se_margeff_mod
    mo2i$marg_eff_enu_CIlower_sortPS  <-  mo2i$marg_eff_enu_sortPS   -  ch$zscore_se_margeff_mod * mo2i$std_err_marg_eff_enu_sortPS
    mo2i$marg_eff_enu_CIupper_sortPS  <-  mo2i$marg_eff_enu_sortPS   +  ch$zscore_se_margeff_mod * mo2i$std_err_marg_eff_enu_sortPS
    
    mo2i$marg_eff_ps_CIlower_sortENU  <-  mo2i$marg_eff_ps_sortENU   -  ch$zscore_se_margeff_mod * mo2i$std_err_marg_eff_ps_sortENU
    mo2i$marg_eff_ps_CIupper_sortENU  <-  mo2i$marg_eff_ps_sortENU   +  ch$zscore_se_margeff_mod * mo2i$std_err_marg_eff_ps_sortENU
    
    mo2i$marg_eff_enu_flag_signi_sortPS  <-  (( mo2i$marg_eff_enu_CIlower_sortPS < 0 ) & (mo2i$marg_eff_enu_CIupper_sortPS < 0 )) |
      (( mo2i$marg_eff_enu_CIlower_sortPS > 0 ) & (mo2i$marg_eff_enu_CIupper_sortPS > 0 ))
    
    mo2i$marg_eff_ps_flag_signi_sortENU   <-  (( mo2i$marg_eff_ps_CIlower_sortENU < 0 ) & (mo2i$marg_eff_ps_CIupper_sortENU < 0 )) |
      (( mo2i$marg_eff_ps_CIlower_sortENU > 0 ) & (mo2i$marg_eff_ps_CIupper_sortENU > 0 ))
    
    
    ## robustness / continutiy check: for cases where the min / max significant values are the actual min / max, check that the bottom 5 / top 5 are all significant (for robustness), else set them to FALSE
    if (  ( min( which( mo2i$marg_eff_enu_flag_signi_sortPS ) ) == 1 ) & any( ! mo2i$marg_eff_enu_flag_signi_sortPS[c(1:5)] ) ) {
      mo2i$marg_eff_enu_flag_signi_sortPS[c(1:5)] <- FALSE
    }  
    
    if (  ( max( which( mo2i$marg_eff_enu_flag_signi_sortPS ) ) == nc$hs ) & any( ! mo2i$marg_eff_enu_flag_signi_sortPS[c( (nc$hs-4) : nc$hs)] ) ) {
      mo2i$marg_eff_enu_flag_signi_sortPS[ c( (nc$hs-4) : nc$hs) ] <- FALSE
    }  
    
    
    if (  ( min( which( mo2i$marg_eff_ps_flag_signi_sortENU ) ) == 1 ) & any( ! mo2i$marg_eff_ps_flag_signi_sortENU[c(1:5)] ) ) {
      mo2i$marg_eff_ps_flag_signi_sortENU[c(1:5)] <- FALSE
    }  
    
    if (  ( max( which( mo2i$marg_eff_ps_flag_signi_sortENU ) ) == nc$hs ) & any( ! mo2i$marg_eff_ps_flag_signi_sortENU[c( (nc$hs-4) : nc$hs)] ) ) {
      mo2i$marg_eff_ps_flag_signi_sortENU[ c( (nc$hs-4) : nc$hs) ] <- FALSE
    }  
    
    mo2i$marg_eff_enu_perc_datapoints_signif  <-  sum ( mo2i$marg_eff_enu_flag_signi_sortPS ) / length ( ll$ns )  
    mo2i$marg_eff_ps_perc_datapoints_signif   <-  sum ( mo2i$marg_eff_ps_flag_signi_sortENU ) / length ( ll$ns )   
    
    
    mo2i$marg_eff_enu_sortPS_ind_first_last_signif   <-   c( min( which( mo2i$marg_eff_enu_flag_signi_sortPS ) ),
                                                             max( which( mo2i$marg_eff_enu_flag_signi_sortPS) ) )
    mo2i$marg_eff_ps_sortENU_ind_first_last_signif   <-   c( min( which( mo2i$marg_eff_ps_flag_signi_sortENU ) ),
                                                             max( which( mo2i$marg_eff_ps_flag_signi_sortENU ) ) )
    
    r_mod_test$sdNS_dENU_ind_first_last_signif[ , nn , pp ]    <- mo2i$marg_eff_enu_sortPS_ind_first_last_signif
    r_mod_test$sdNS_dPS_ind_first_last_signif[ , nn , pp ]     <- mo2i$marg_eff_ps_sortENU_ind_first_last_signif
    
    mo2i$marg_eff_enu_sortPS_percentiles_first_last_signif   <-   round( mo2i$marg_eff_enu_sortPS_ind_first_last_signif * 100 / nc$hs )
    mo2i$marg_eff_ps_sortENU_percentiles_first_last_signif   <-   round( mo2i$marg_eff_ps_sortENU_ind_first_last_signif * 100 / nc$hs )
    
    
    ### export into results variable
    r_mod$dNS_dPS_norm_imprNS_sortENU          [ pp , nn ,   ]            <-  mo2i$marg_eff_ps_sortENU * g$sign_normaliser_imprNS_dNS_dPS_u[ nn , pp]
    r_mod$dNS_dPS_is_signif_sortENU[ pp , nn ,   ]                        <-  mo2i$marg_eff_ps_flag_signi_sortENU 
    
    ### ----- prepare predictions at representative values ------ ####
    
    ll$ps_mean   <-  mean (  ll$ps ) # this should be zero, but oh well
    ll$ps_median   <-  median (  ll$ps ) 
    ll$enu_mean  <-  mean ( ll$enu ) # this should be zero, but oh well
    
    mo2i$ind_of_mean_in_ps_sortPS     <-  which( abs( ll$ps_sortPS - ll$ps_mean ) == min( abs( ll$ps_sortPS - ll$ps_mean ) ) )[1]  # index of the mean of PS ; [1] is just in case of ties, as is the case with infra
    mo2i$perc_of_mean_in_ps_sortPS    <-  round ( mo2i$ind_of_mean_in_ps_sortPS * 100 / nc$hs )
    
    mo2i$ind_of_mean_in_enu_sortENU     <-  which( abs( ll$enu_sortENU - ll$enu_mean ) == min( abs( ll$enu_sortENU - ll$enu_mean ) ) )[1]  # index of the mean of PS
    mo2i$perc_of_mean_in_enu_sortENU    <-  round ( mo2i$ind_of_mean_in_enu_sortENU * 100 / nc$hs )
    
    if( ! tf$ps_u_tf_use[ pp ] == "sat" ){
      
      mo2i$min_PS_with_signi_dNS_dENU  <-  ll$ps_sortPS[ mo2i$marg_eff_enu_sortPS_ind_first_last_signif[1] ]
      mo2i$max_PS_with_signi_dNS_dENU  <-  ll$ps_sortPS[ mo2i$marg_eff_enu_sortPS_ind_first_last_signif[2] ]
      
      mo2i$perc_of_min_PS_with_signi_dNS_dENU  <-  mo2i$marg_eff_enu_sortPS_percentiles_first_last_signif[1]
      mo2i$perc_of_max_PS_with_signi_dNS_dENU  <-  mo2i$marg_eff_enu_sortPS_percentiles_first_last_signif[2]
      
    }
    
    ### need to reverse the order for those ps variables that have been sat-transformed (all sat-transformed are max-type = sign-inverting! )
    
    if( tf$ps_u_tf_use[ pp ] == "sat" )  {
      
      mo2i$min_PS_with_signi_dNS_dENU  <-  ll$ps_sortPS[ mo2i$marg_eff_enu_sortPS_ind_first_last_signif[2] ]
      mo2i$max_PS_with_signi_dNS_dENU  <-  ll$ps_sortPS[ mo2i$marg_eff_enu_sortPS_ind_first_last_signif[1] ]
      
      mo2i$perc_of_min_PS_with_signi_dNS_dENU  <-  ( 100 - mo2i$marg_eff_enu_sortPS_percentiles_first_last_signif[2] ) + 1
      mo2i$perc_of_max_PS_with_signi_dNS_dENU  <-  ( 100 - mo2i$marg_eff_enu_sortPS_percentiles_first_last_signif[1] ) + 1
      
      mo2i$perc_of_mean_in_ps_sortPS   <-  100 - mo2i$perc_of_mean_in_ps_sortPS + 1
    }
    
    
    mo2i$is_margeff_enu_at_ps_mean_signi <-
      ( mo2i$ind_of_mean_in_ps_sortPS  >  mo2i$marg_eff_enu_sortPS_ind_first_last_signif[1] ) &
      ( mo2i$ind_of_mean_in_ps_sortPS  <  mo2i$marg_eff_enu_sortPS_ind_first_last_signif[2] )
    
    
    mo2i$b3_gate  <-  (summary(mo2i))$coefficients[4,4]  < 0.05
    
    ### ----- predictions at representative values of PS: NS = f (ENU) , m(PS) ------ ####
    # If dNS/dENU is not significant for any PS, then mo2i$max_PS_with_signi_dNS_dENU will be NaN
    
    
    mo2i$ypred$NSpred_fENU_at_min_signi_PS  <-
      mo2i$a +   mo2i$b2_ps * mo2i$min_PS_with_signi_dNS_dENU  +
      ( mo2i$b3_int  * mo2i$min_PS_with_signi_dNS_dENU + mo2i$b1_enu ) * ll$enu
    
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p1os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p1os  +
      ( mo2i$b3_int  * ll$ps_fs_p1os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p5os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p5os  +
      ( mo2i$b3_int  * ll$ps_fs_p5os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p10os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p10os  +
      ( mo2i$b3_int  * ll$ps_fs_p10os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p20os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p20os  +
      ( mo2i$b3_int  * ll$ps_fs_p20os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p25os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p25os  +
      ( mo2i$b3_int  * ll$ps_fs_p25os + mo2i$b1_enu ) * ll$enu
    
    
    mo2i$ypred$NSpred_fENU_at_max_signi_PS  <-
      mo2i$a  +   mo2i$b2_ps * mo2i$max_PS_with_signi_dNS_dENU +
      (mo2i$b3_int  * mo2i$max_PS_with_signi_dNS_dENU + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p100os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p100os  +
      ( mo2i$b3_int  * ll$ps_fs_p100os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p95os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p95os  +
      ( mo2i$b3_int  * ll$ps_fs_p95os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p90os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p90os  +
      ( mo2i$b3_int  * ll$ps_fs_p90os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p80os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p80os  +
      ( mo2i$b3_int  * ll$ps_fs_p80os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p75os  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_fs_p75os  +
      ( mo2i$b3_int  * ll$ps_fs_p75os + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_mean_PS  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_mean +
      ( mo2i$b3_int  * ll$ps_mean + mo2i$b1_enu ) * ll$enu
    
    mo2i$ypred$NSpred_fENU_at_median_PS  <-
      mo2i$a +   mo2i$b2_ps * ll$ps_p50 +
      ( mo2i$b3_int  * ll$ps_p50 + mo2i$b1_enu ) * ll$enu
    
    ##### ----------- export results ------------------- #####
    
    
    r_mod$NSpred_fs_PSmax_minus_PSmin_sortENU[ pp , nn ,  ]  <-  ( mo2i$ypred$NSpred_fENU_at_PSfs_p100os [ ll$ind_sortENU ] - 
                                                                     mo2i$ypred$NSpred_fENU_at_PSfs_p1os[ ll$ind_sortENU ] ) * 
      g$sign_normaliser_imprNS_for_NSpred_fs_PSmaxsg_minus_PSminsg_m [ nn ]
    
    
    r_mod$NSpred_fs_PSp90_minus_PSp10_sortENU[ pp , nn ,  ]  <-  ( mo2i$ypred$NSpred_fENU_at_PSfs_p90os [ ll$ind_sortENU ] - 
                                                                     mo2i$ypred$NSpred_fENU_at_PSfs_p10os[ ll$ind_sortENU ] ) * 
      g$sign_normaliser_imprNS_for_NSpred_fs_PSmaxsg_minus_PSminsg_m [ nn ]
    
    
    r_mod$flag_ENU_where_eff_ps_signif_sortENU[ pp , nn ,   ]    <-   mo2i$marg_eff_ps_flag_signi_sortENU
    
    
    
    r_mod$NSpred_fs_PSmaxsg_minus_PSminsg_sortENU[ pp , nn ,  ]  <-  ( mo2i$ypred$NSpred_fENU_at_max_signi_PS[ ll$ind_sortENU ] - 
                                                                         mo2i$ypred$NSpred_fENU_at_min_signi_PS[ ll$ind_sortENU ] ) * 
      g$sign_normaliser_imprNS_for_NSpred_fs_PSmaxsg_minus_PSminsg_m [ nn ]
    
    
    r_mod$flag_ps_signif_sortENU[ pp , nn ,   ]  <-  rep(  ( ( mo2i$marg_eff_enu_sortPS_ind_first_last_signif[1] < 300 )
                                                             & ( mo2i$marg_eff_enu_sortPS_ind_first_last_signif[2] > 0 ) ) &
                                                             (   mo2i$ps_signi_b2b3joint  <  ch$th_p_mod_PS_b2b3joint  ) , nc$hs )
    
    ### ---------- BACK-TRAFOS to original space (os) ----------- ###
    
    
    if (  tf$ns_m_tf_use[ nn ] == "lin" ) {   # for linear = identical ( = no ) transformation of NS variable
      
      ## NS = f (ENU), m(PS)
      
      mo2i$ypred$enu_only_from_blr_retrafo_sortENU  <-
        ( ( ( mo1e$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_mean_PS_retrafo_sortENU       <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_mean_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_median_PS_retrafo_sortENU       <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_median_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_min_signi_PS_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_min_signi_PS * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p5os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p1os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p10os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p20os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p20os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p25os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p25os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_max_signi_PS_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_max_signi_PS * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p100os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p95os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p90os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p80os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p80os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p75os_retrafo_sortENU  <-
        ( ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p75os * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_ENUobs_PSobs_retrafo_sortENU  <-
        ( ( ( mo2i$fitted.values * st$ns_m_sd[ nn ] )  + st$ns_m_means[ nn ] ) - tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
    }
    
  
    
    if (  tf$ns_m_tf_use[ nn ] == "log" ) {   # for logarithmic transformation of NS variable
      
      
      ## NS = f (ENU), m(PS)
      
      mo2i$ypred$enu_only_from_blr_retrafo_sortENU  <-  ( exp(
        (  mo1e$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )  -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_mean_PS_retrafo_sortENU       <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_mean_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )   -  tf$ns_m_offsets[[ nn ]] )  [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_median_PS_retrafo_sortENU       <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_median_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )   -  tf$ns_m_offsets[[ nn ]] )  [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_min_signi_PS_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_min_signi_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p1os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p5os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p10os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p20os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p20os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p25os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p25os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_max_signi_PS_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_max_signi_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p100os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p95os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p90os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p80os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p80os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p75os_retrafo_sortENU  <-  ( exp( (
        mo2i$ypred$NSpred_fENU_at_PSfs_p75os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ]  ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_ENUobs_PSobs_retrafo_sortENU  <-  ( exp((
        mo2i$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) -  tf$ns_m_offsets[[ nn ]] ) [ ll$ind_sortENU ]
      
      
    }
    
  
    
    
    if (  tf$ns_m_tf_use[ nn ] == "sat" ) {   # for saturation transformation of NS variable
      
      
      ## NS = f (ENU), m(PS)
      
      mo2i$ypred$enu_only_from_blr_retrafo_sortENU <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]  +  g$ns_m_sign_for_sat_retrafo[ nn ]  *
            exp((( mo1e$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_mean_PS_retrafo_sortENU   <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ]  *
            exp(((  mo2i$ypred$NSpred_fENU_at_mean_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_median_PS_retrafo_sortENU   <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ]  *
            exp(((  mo2i$ypred$NSpred_fENU_at_median_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )) ) [ ll$ind_sortENU ]
      
      
      
      mo2i$ypred$NSpred_fENU_at_min_signi_PS_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp(( mo2i$ypred$NSpred_fENU_at_min_signi_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] )  ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p5os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p1os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p10os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p20os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p20os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p25os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p25os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_fENU_at_max_signi_PS_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]    +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_max_signi_PS * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p100os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p95os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p90os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p80os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p80os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      mo2i$ypred$NSpred_fENU_at_PSfs_p75os_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]   +  g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$ypred$NSpred_fENU_at_PSfs_p75os * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      
      mo2i$ypred$NSpred_ENUobs_PSobs_retrafo_sortENU  <-
        ( tf$ns_m_sat_val[[ nn ]]  -  tf$ns_m_offsets[[ nn ]]  +   g$ns_m_sign_for_sat_retrafo[ nn ] *
            exp((( mo2i$fitted.values * st$ns_m_sd[ nn ] ) + st$ns_m_means[ nn ] ) ) ) [ ll$ind_sortENU ]
      
      
    }
    ### prediction and back-transform finished ####
    
    
    #### export results
    
    r_mod$NSpred_os_PSmax_minus_PSmin_percrange_sortENU[ pp , nn ,   ]  <-  ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_sortENU  - 
                                                                                  mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_sortENU) *100 / ll$ns_os_range ) * 
      g$ns_m_more_is_better_as_sign [ nn ]
    
    r_mod$NSpred_os_PSmaxsg_minus_PSminsg_percrange_sortENU[ pp , nn ,   ]  <-  ( ( mo2i$ypred$NSpred_fENU_at_max_signi_PS_retrafo_sortENU  - 
                                                                                      mo2i$ypred$NSpred_fENU_at_min_signi_PS_retrafo_sortENU) *100 / ll$ns_os_range ) * 
      g$ns_m_more_is_better_as_sign[ nn ]
    
    
    r_mod$NSpred_os_PSp90_minus_PSp10_percrange_sortENU[ pp , nn ,  ]  <-  ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_sortENU  - 
                                                                                 mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_sortENU) *100 / ll$ns_os_range ) * 
      g$ns_m_more_is_better_as_sign [ nn ]
    
    r_mod$NSpred_os_PSp95_minus_PSp5_percrange_sortENU[ pp , nn ,   ]  <-  ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_sortENU  - 
                                                                                 mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_sortENU) *100 / ll$ns_os_range ) * 
      g$ns_m_more_is_better_as_sign [ nn ]
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_cutoff_sortENU  <- mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_sortENU
    mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_cutoff_sortENU > a$ns_ceiling[nn] ] <- a$ns_ceiling[nn]
    mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_cutoff_sortENU < a$ns_floor[nn] ] <- a$ns_floor[nn]
    
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_cutoff_sortENU  <- mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_sortENU
    mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_cutoff_sortENU > a$ns_ceiling[nn] ] <- a$ns_ceiling[nn]
    mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_cutoff_sortENU < a$ns_floor[nn] ]   <- a$ns_floor[nn]
    
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_cutoff_sortENU  <- mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_sortENU
    mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_cutoff_sortENU > a$ns_ceiling[nn] ] <- a$ns_ceiling[nn]
    mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_cutoff_sortENU < a$ns_floor[nn] ] <- a$ns_floor[nn]
    
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_cutoff_sortENU  <- mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_sortENU
    mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_cutoff_sortENU > a$ns_ceiling[nn] ] <- a$ns_ceiling[nn]
    mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_cutoff_sortENU < a$ns_floor[nn] ]   <- a$ns_floor[nn]
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_cutoff_sortENU  <- mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_sortENU
    mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_cutoff_sortENU > a$ns_ceiling[nn] ] <- a$ns_ceiling[nn]
    mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_cutoff_sortENU < a$ns_floor[nn] ] <- a$ns_floor[nn]
    
    
    mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_cutoff_sortENU  <- mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_sortENU
    mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_cutoff_sortENU > a$ns_ceiling[nn] ] <- a$ns_ceiling[nn]
    mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_cutoff_sortENU [  mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_cutoff_sortENU < a$ns_floor[nn] ]   <- a$ns_floor[nn]
    
    
    r_mod$NSpred_os_PSmax_minus_PSmin_percrange_cutoff_sortENU[ pp , nn ,  ] <-  ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p100os_retrafo_cutoff_sortENU  - 
                                                                                       mo2i$ypred$NSpred_fENU_at_PSfs_p1os_retrafo_cutoff_sortENU) *100 / ll$ns_os_range ) * 
      g$ns_m_more_is_better_as_sign [ nn ]
    
    
    r_mod$NSpred_os_PSp90_minus_PSp10_percrange_cutoff_sortENU[ pp , nn ,  ] <-  ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p90os_retrafo_cutoff_sortENU  - 
                                                                                       mo2i$ypred$NSpred_fENU_at_PSfs_p10os_retrafo_cutoff_sortENU) *100 / ll$ns_os_range ) * 
      g$ns_m_more_is_better_as_sign [ nn ]
    
    
    r_mod$NSpred_os_PSp95_minus_PSp5_percrange_cutoff_sortENU[ pp , nn ,  ] <-  ( ( mo2i$ypred$NSpred_fENU_at_PSfs_p95os_retrafo_cutoff_sortENU  - 
                                                                                      mo2i$ypred$NSpred_fENU_at_PSfs_p5os_retrafo_cutoff_sortENU) *100 / ll$ns_os_range ) * 
      g$ns_m_more_is_better_as_sign [ nn ]
    
  }
} ##### end of mega-loop ####
```


```{r kstest}
r_mod$kstest_below_th <-  r_mod$kstest  <  ch$th_p_KS
r_bvr_ks$kstest_below_th <-  r_bvr_ks$kstest  <  ch$th_p_KS

r_mod$kstest_allow_for_agg  <- array( data = NA , dim = c ( nv$ps_u , nv$ns_m , nc$hs ) )

for (pp in 1:nv$ps_u){
  for ( nn in 1:nv$ns_m ){ 
    
    r_mod$kstest_allow_for_agg[ pp , nn  , ]  <-  rep ( ! r_mod$kstest_below_th[ pp , nn ] , nc$hs )
  }
}
```

```{r histograms}
##### histograms of pooled effects
ll$total_cases_per_ps <-   length( nv$ns_m ) * 1 * nc$hs  

ll$limit <-  ceiling( 100 / ll$int ) * ll$int
ll$break_seq <- seq( from = -1 * ll$limit  , to = 1 * ll$limit  , by = ll$int   )


ll$ps_overall_effect_percrange_PSmaxminsg_signi  <- r_mod$NSpred_os_PSmaxsg_minus_PSminsg_percrange_sortENU 

ll$ps_overall_effect_percrange_PSmaxminsg_signi [ ! r_mod$flag_ENU_where_eff_ps_signif_sortENU ]  <- NA

ll$ps_overall_effect_percrange_PSmaxminsg_signi_cut <- ll$ps_overall_effect_percrange_PSmaxminsg_signi

ll$ps_overall_effect_percrange_PSmaxminsg_signi_cut[ 
  ( ll$ps_overall_effect_percrange_PSmaxminsg_signi < -100 )  |  ( ll$ps_overall_effect_percrange_PSmaxminsg_signi > 100 ) ]  <- NA

for ( pp in 1:length( nv$ps_u ) ) {        
  ll$freq_max[ppi] <-  max( hist( ll$ps_overall_effect_percrange_PSmaxminsg_signi_cut[ pp ,  , ], 
                                  breaks = ll$break_seq , plot = FALSE )$counts , na.rm = TRUE)
}

ll$freq_perc_max <- max ( ll$freq_max / ll$total_cases_per_ps ) * 100

ll$cPS_hist_obj_pos <- hist (  ll$ps_overall_effect_percrange_PSmaxminsg_signi_cut[ pp ,  , ][
  ll$ps_overall_effect_percrange_PSmaxminsg_signi_cut[ pp ,  , ] > 0 ] ,
  breaks = ll$break_seq , plot = FALSE ) 

ll$cPS_hist_obj_neg <- hist (  ll$ps_overall_effect_percrange_PSmaxminsg_signi_cut[ pp ,  , ][
  ll$ps_overall_effect_percrange_PSmaxminsg_signi_cut[ pp ,  , ] < 0 ]  ,
  breaks = ll$break_seq , plot = FALSE ) 

# divide counts by total number of cases per PS to get fraction of cases, expressed as percentage
ll$cPS_hist_obj_pos$counts   <-  ( ll$cPS_hist_obj_pos$counts /  ll$total_cases_per_ps ) * 100
ll$cPS_hist_obj_neg$counts   <-  ( ll$cPS_hist_obj_neg$counts /  ll$total_cases_per_ps ) * 100
```


```{r multivariate}
##### multi-variate (3-PF) models

for( nn in 1: g$l_n ){
  
  mvr$mo_full       <-   lm ( ns_m[ , nn ]  ~  enu_m +  ps_m$gini  +  ps_m$resrent  + ps_m$gov   )
  mvr$mo_full_rob   <-   lm_robust ( ns_m[ , nn ]  ~  enu_m  +  ps_m$gini  +  ps_m$resrent  + ps_m$gov  , se_type = sw$HC )
  
  
  mvr$kstest_pval[ nn  ]  <- ks.test ( sort( mvr$mo_full$residuals ) , "pnorm",  0 , sd (  mvr$mo_full$residuals  ) )$p.value
  
  mvr$b1_enu[ nn  ]       <-  summary ( mvr$mo_full )$coefficient[ 2 , 1 ]
  mvr$b2_gini[ nn]      <-  summary ( mvr$mo_full )$coefficient[ 3 , 1 ]
  mvr$b3_resrent[ nn  ]   <-  summary ( mvr$mo_full )$coefficient[ 4 , 1 ]
  mvr$b4_gov[ nn ]       <-  summary ( mvr$mo_full )$coefficient[ 5 , 1 ]
  
  mvr$p_b1_enu[ nn ]      <-  summary ( mvr$mo_full_rob )$coefficient[ 2 , 4 ]
  mvr$p_b2_gini[ nn  ]     <-  summary ( mvr$mo_full_rob )$coefficient[ 3 , 4 ]
  mvr$p_b3_resrent[ nn  ]  <-  summary ( mvr$mo_full_rob )$coefficient[ 4 , 4 ]
  mvr$p_b4_gov[ nn ]      <-  summary ( mvr$mo_full_rob )$coefficient[ 5 , 4 ]
  
  mvr$mo_no_enu        <-   lm ( ns_m[ , nn ]  ~  ps_m$gini  +  ps_m$resrent  + ps_m$gov   )
  mvr$mo_no_gini       <-   lm ( ns_m[ , nn ]  ~  enu_m +  ps_m$resrent + ps_m$gov   )
  mvr$mo_no_resrent    <-   lm ( ns_m[ , nn ]  ~  enu_m +  ps_m$gini    + ps_m$gov   )
  mvr$mo_no_gov        <-   lm ( ns_m[ , nn ]  ~  enu_m +  ps_m$gini    +  ps_m$resrent   )
  
  mvr$r2_adj_mvr[ nn  ]    <-      summary ( mvr$mo_full )$adj.r.squared
  mvr$r2_adj_bvr[ nn  ]    <-      summary ( lm ( ns_m[ , nn ]  ~  enu_m) )$adj.r.squared
  
  
  mvr$f2 [ 1, nn   ]   <-   ( summary( mvr$mo_full )$r.squared  -  summary( mvr$mo_no_enu )$r.squared ) /
    ( 1 - summary( mvr$mo_full )$r.squared ) 
  mvr$f2 [ 2, nn   ]   <-   ( summary( mvr$mo_full )$r.squared  -  summary( mvr$mo_no_gini )$r.squared ) /
    ( 1 - summary( mvr$mo_full )$r.squared ) 
  mvr$f2 [ 3, nn   ]   <-   ( summary( mvr$mo_full )$r.squared  -  summary( mvr$mo_no_resrent )$r.squared ) /
    ( 1 - summary( mvr$mo_full )$r.squared ) 
  mvr$f2 [ 4 , nn  ]   <-   ( summary( mvr$mo_full )$r.squared  -  summary( mvr$mo_no_gov )$r.squared ) /
    ( 1 - summary( mvr$mo_full )$r.squared ) 
  
  for ( ii in 1:4 ) { 
    mvr$power [ ii , nn  ]   <-  wp.regression( n = nc$hs, p1 = 4 , p2 = 3 , f2 = mvr$f2 [ ii , nn  ] ,
                                                alpha = 0.05, power = NULL)$power
  }
  
}
```
